A free/open-source Kazakh-Tatar machine translation system

### 2013-04-07 paper/paper.tex
a syntactic difference

\subsection{Morphotactic differences}
2 or 3 specific examples
\subsection{Lexical and morphological differences}
2 or 3 specific examples
\subsection{Syntactic differences}
2 or 3 specific examples
> ұна- vs.\ ярат- (does this count as syntactic?)

>>>>

\subsection{Morphotactic differences}
2 or 3 specific examples
\subsection{Lexical and morphological differences}
2 or 3 specific examples
\subsection{Syntactic differences}
%2 or 3 specific examples
There aer a number of syntactic differences in Tatar and Kazakh, which include differences in verb valencies in equivalent translations, FIXME, and FIXME.

%FIXME: Ilnar, please check the Tatar
An example of a difference in verb valencies is with the expression corresponding to ``to like something'' in Kazakh and Tatar.  In Kazakh, the verb ‹ұна› is used, e.g. ‹оқу маған ұнайды› ``I like studying'', where the subject ``I'' in English is expressed through a dative experiencer in Kazakh and the object ``study'' in English is the grammatical subject in Kazakh.  Tatar, on the other hand, uses a verb whose arguments correspond to the arguments of ``to like'' in English, e.g. ‹мин укуны яратам› ``I like studying'', where the first person pronoun is the grammatical subject and ``studying'' is the grammatical direct object.
%(does this count as syntactic?)
